%-------------------------
% Resume in LaTeX
% Author : Duy La
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.6in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Large \scshape Duy La} \\ \vspace{1pt}
    19915 Creek Bend Trail, Houston, Texas 77084 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 832-983-1588 ~ \href{mailto:duyvietla@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{duyvietla@gmail.com}} ~ 
    \href{https://linkedin.com/in/duy-la/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/duy-la}}  ~
    \href{https://github.com/aylud}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/aylud}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Houston}{August 2021 -- December 2024}
      {Bachelor of Business Administration in Management Information Systems}{Houston, TX}
      \resumeItemListStart
        \resumeItem{Cumulative GPA: 3.72}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Copeland}{August 2023 -- December 2023}
      {IT/AV Co-op Position }{Sidney, OH}
      \resumeItemListStart
        \resumeItem{Manage IT/AV operations, including meeting room preparation for 30+ conference rooms on site, video production/editing for 50+ corporate events, and systems troubleshooting regarding AV/EV equipment.}
        \resumeItem{Assist with management and technical operations of 70+ international call centers through call flow diagramming, contributing to efficient customer service and team communication globally while saving the company over \$70,000 per call flow utilizing SaaS built off of AWS.}
        \resumeItem{Collaborate in process optimization efforts, including the development of IT/AV reporting infrastructure in ServiceNow ESM, dashboards, and SharePoint web pages facilitating smooth transition to independent private company.}
      \resumeItemListEnd

     \resumeSubheading
       {The Alley}{June 2022 -- August 2023}
       {Front of House}{Katy, TX}
      \resumeItemListStart
        \resumeItem{Facilitated 1000+ premium customer interactions daily through strategic oversight and orchestration of team operations.}
        \resumeItem{Drove inventory turnover of 50+ products, to optimize merchandise and produce and support cross-functional teams of up to 10 members.}
        \resumeItem{Innovatively tested and launched 10+ new menu items, enhancing product portfolio for annual events.}
      \resumeItemListEnd


    \resumeSubheading
      {Ding Tea}{February 2021 - May 2022}
      {Shift Lead}{Katy, TX}
      \resumeItemListStart
        \resumeItem{Increased operational efficiency leveraging Microsoft Office Suite for data-driven decision-making in employee and shift management.}
        \resumeItem{Ensured top-notch quality for produce shipments through close collaboration with franchise stakeholders.}
        \resumeItem{Boosted brand presence via data-driven social media strategies, achieving 100\% growth in followership.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Academic Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{NOV Supply Chain Cost Strategies} $|$ Excel, PowerPoint}{April 2023}
          \resumeItemListStart
            \resumeItem{Collaborated to analyze and present supply chain strategies for sourcing quality steel in key market areas to executive employees at National Oilwell Varco.}
            \resumeItem{Developed sophisticated Excel cost tool, employing advanced functions and macros, to model and optimize supply chain costs and efficiency.}
            \resumeItem{Employed Kanban-style visual management and timeboxing approach to streamline project workflow, ensuring seamless team coordination and adherence to timelines. }
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Plant Shop Simulator} $|$ \emph{Java}}{April 2023}
          \resumeItemListStart
            \resumeItem{Developed Java-based simulator for basic plant shop, with interactive user interface. }
            \resumeItem{Implemented effective use of Java packages to create a functional application, enhancing understanding of object-oriented programming principles. }
            \resumeItem{Engineered system to handle selection of plant types, assigning values, and calculating store profits based on varying order sizes.}
          \resumeItemListEnd 
          \vspace{-13pt}
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Software and Systems}{: Java, Python, Microsoft Excel, Microsoft PowerPoint, Microsoft SharePoint, Genesys Cloud, ServiceNow, Linux, LaTeX, MatLab } \\
     \textbf{Technical}{: Soldering, Cybersecurity Basics, Network Management, High-Performance and Cluster Computing Fundamentals, SLURM Batch Scheduling} \\
     \textbf{Methodologies}{: Systems Development Life Cycle (SDLC), Agile, Waterfall, Critical Path Method, Kanban, Data Analysis, and Business Process Modeling } \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Friends of Medecins Sans Frontieres}{August 2022 - Present}{Vice-President}{University of Houston}
           \vspace{5pt}
            \resumeItemListStart
                \resumeItem{Orchestrated speaker events and directed club logistics using project management tools}
                \resumeItem{Raised awareness and financial support for the organization through data-driven marketing and fundraising initiatives. }
                \resumeItem{Led organization of 30+ members to promote community service, academics, and unity.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
